---
title: "ggplot intro"
author: "Emily"
date: "13 July 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Plan

We'll load libraries and learn ggplot2.

Here we write in Markdown.

# hastags mean headers 

two hashtags were used infront of ## Plan, but we can use them in the middle of a line, and they have no effect.

```{r}
# here we write R.

# hashtags mean comment
summary(cars)
```

# Load libraries
```{r}
# Loading my libraries
library(dplyr)
library(gapminder)
library(ggplot2) # install.packages('ggplot2')

## subset our data
g <- gapminder %>%
  filter(year == 2007) %>%
  mutate(pop_m = pop/1e6)
```

# My first plot
a simple geom_point
```{r}
## ggplot needs data (g), aes(x = , y = ) + what kind of plot
s <- ggplot(g, aes(x = gdpPercap, y = lifeExp)) + geom_point() # actually works better with everything on the same line
s # to print the plot
```

# My Seconf plot
a simple geom_point with aes()
```{r}
## ggplot(data, aes(what's x, what's y)) + waht kind of plot

s2 <-  s + aes(size = pop_m)
s2

s3 <-  s2 + aes(colour = continent)
s3
```


# nice plus signs (sort of like piping!)

```{r}
s <- ggplot(g, aes(x = gdpPercap, y = lifeExp)) + 
  geom_point() + 
  aes(size = pop_m) + 
  aes(colour = continent) +
  ggtitle('Health and Wealth of Nations in 2007') +
  xlab('GDP per capita (USD/year)') +
  ylab('Life expectancy (years)') +
  scale_colour_discrete('Continent') +
  scale_size_continuous('Population (m)')
s # how to put it into one object, rather than 3 and add loads more stuff!
```

# Make a boxplot
This is my boxplot of continent and life expectancy.
Using `g` which is a subset of 2007

```{r}
b <- ggplot(g, aes(x = continent, y = lifeExp)) + # remember to put ggplot first, then after x and y, say what plot you want
  geom_boxplot() +
  aes(fill = continent) +
  theme(legend.position = 'none')
b
  
```


# GoogleVis interactive figure
```{r}
#install.packages('googleVis')
suppressPackageStartupMessages(library(googleVis))

```

```{r, results='asis'}
op <- options(gvis.plot.tag='chart') ## results='asis' is very important

m = gvisMotionChart(
  g,
  idvar='country', 
  timevar='year', 
  xvar='log_gdpPercap', 
  yvar='lifeExp', 
  colorvar='continent',
  sizevar='pop_m')
plot(m)


```

